---
title: "Cabbages"
author: "Emery Simon"
date: "2/25/2025"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


We looked at the variables and it looled like we had numerical variables which is the numerical variable that's going to be how much vitc (this is a numerical variable) is contained between the two cultivation methods. Those cultivation methods are c39 and c52 methods and those are the categorical variables. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

Box c52 is higher than c39, which means the first Quartile of c52 is larger than c39 and that concludes that they are statistically different. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The first Quartile of c39 is at 46 and c52 is at 58. Both contain 30 numerical values.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
t.test(VitC~Cult,data=veggy)
```

I reject the null hypothesis because the chamces are an extremely small number and that chance is 0.00000003405 and conclude that c39 and c52 are significantly different.

# Discussion and Conclusion

We first examined the boxplot for VitC adn found the difference in average between c39 and c52. We also found that they are statistically different. We then examined the numerical results in which we found the values of c39 and c52. Lastly, we wrote the hypothesis in inferential results which we rejected the null hypothesis because the chances were extremely low. This made c39 and c52 significantly different.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
